Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-03-26 supplement.tex
Ready for feeback by @Giappo
Fix itemization in supmat

For all experiments, the intermediate results can all be downloaded 
from their respective websites.

@@

\itemize{
  \item the use of 20 replicates results in decent plots
  \item the use of more taxa, counterintuitively, increases the inference error
  \item the use of longer DNA sequences, as expected, decreases the inference error
  \item {
    there is a difference when a twin alignment is selected to have
    an equal amount of mutations as the true alignment. The consequences
    of this is unknown
  }
  \item {
    using a mutation rate less than 1.0 / crown age, decreases the
    inference error. We predict this will increase the error in the parameter
    estimation
  }
}

>>>>

For all experiments, the intermediate results can all be downloaded 
from their respective websites, which is approximately 5 gigabyte in total.

@@

\itemize{
  \item{
    the use of 20 replicates results in decent plots
  }
  \item{
    the use of more taxa, counterintuitively, increases the inference error
  }
  \item{
    the use of longer DNA sequences, as expected, decreases the inference error
  }
  \item{
    there is a difference when a twin alignment is selected to have
    an equal amount of mutations as the true alignment. The consequences
    of this is unknown
  }
  \item{
    using a mutation rate less than 1.0 / crown age, decreases the
    inference error. We predict this will increase the error in the parameter
    estimation
  }
}
